Designing Types for R, Empirically

### 2020-10-15 paper/main.tex
merge

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}   %% For author/year citations
\usepackage{my_style}
\usepackage{listings, wrapfig,xspace}
\usepackage{paralist}
\usepackage{booktabs} % To thicken table lines
\usepackage{makecell}

@@

\begin{table}[H]
	\centering
	\resizebox{.98\linewidth}{!}{
		\begin{tabular}{llrrr}
			\toprule
			Merge Strategy & Function Type \\
			\midrule
			Union of Arrows &  \makecell[tl]{
		      \FUN{\CLASS{{\tt data.frame}}, ...}{\CLASS{{\tt data.frame}}}	| \\
             \FUN{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}} | \\
             \FUN{\CLASS{{\tt data.frame, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, tbl, tbl\_df}}}
			} \\
		\addlinespace
			Hybrid & \makecell[tl]{
				\FUN{\CLASS{{\tt data.frame}}, ...}{\CLASS{{\tt data.frame}}}	| \\
				\FUN{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}} | \\
				\FUN{\CLASS{{\tt data.frame, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, tbl, tbl\_df}}}
			} \\
		\addlinespace
			Arrow of Unions & \makecell[tl]{
				$\langle \CLASS{{\tt data.frame}} \;|\; \CLASS{{\tt data.frame, tbl, tbl\_df}} \;|\; \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}, ...} \rangle$ $\rightarrow$ \\
				$\CLASS{{\tt data.frame}} \;|\; \CLASS{{\tt data.frame, tbl, tbl\_df}} \;|\; \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}$
			} \\
			\bottomrule
	\end{tabular}}
	\caption{Types of \code{dplyr::rename} with different type merge strategies. }\label{tbl:real-function-different-merge-strats-2}
\end{table}

>>>>

\bibliographystyle{ACM-Reference-Format}
\citestyle{acmauthoryear}   %% For author/year citations
\usepackage{my_style}
\usepackage{listings, wrapfig,xspace}
\usepackage{paralist}
\usepackage{booktabs} % To thicken table lines
\usepackage{makecell}
\usepackage{microtype}

@@

\begin{table}[H]
	\centering
	\resizebox{.98\linewidth}{!}{
		\begin{tabular}{llrrr}
			\toprule
			Merge Strategy & Function Type \\
			\midrule
			Union of Arrows &  \makecell[tl]{
		      \FUN{\CLASS{{\tt data.frame}}, ...}{\CLASS{{\tt data.frame}}}	| \\
             \FUN{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}} | \\
             \FUN{\CLASS{{\tt data.frame, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, tbl, tbl\_df}}}
			} \\
		\addlinespace
			Hybrid & \makecell[tl]{
				\FUN{\CLASS{{\tt data.frame}}, ...}{\CLASS{{\tt data.frame}}}	| \\
				\FUN{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}} | \\
				\FUN{\CLASS{{\tt data.frame, tbl, tbl\_df}}, ...}{\CLASS{{\tt data.frame, tbl, tbl\_df}}}
			} \\
		\addlinespace
			Arrow of Unions & \makecell[tl]{
				$\langle \CLASS{{\tt data.frame}} \;|\; \CLASS{{\tt data.frame, tbl, tbl\_df}} \;|\; \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}, ... \rangle$ $\rightarrow$ \\
				$\CLASS{{\tt data.frame}} \;|\; \CLASS{{\tt data.frame, tbl, tbl\_df}} \;|\; \CLASS{{\tt data.frame, grouped\_df, tbl, tbl\_df}}$
			} \\
			\bottomrule
	\end{tabular}}
	\caption{Types of \code{dplyr::rename} with different type merge strategies. }\label{tbl:real-function-different-merge-strats-2}
\end{table}
